TADCompare: an R package for differential analysis and characterization of Topologically Associated Domains

### 2019-09-24 manuscript/manuscript.Rmd
make more up to date

To test whether each slope is significantly different than random, we used a permutation test. For phenotype $i$ with the gene network of size $g_i$, we define $\beta_i$ as the slope derived by regressing the external degree distribution on the internal degree distribution. We then generate $n=10000$ networks of randomly selected genes of the same size $g_i$ as the set for phenotype $i$. For each random network $j$, we identify its slope $\beta_{r}$ representing the internal vs. external degree distribution regression line of random coherence. We calculate the permutation p-value as $p_i = \frac{(\sum_{j=1}^nI({\beta_{rj} > \beta_i}) + 1}{n + 1}$ [@Phipson:2010aa]. Intuitively, this approach estimates whether the slope of the phenotype-specific network $\beta_i$ is consistently larger than those of random networks. All analyses and visualizations were performed in the R/Bioconductor computing environment v.3.4.0 [@gentleman2006bioinformatics].

>>>>

To test whether each slope is significantly different than random, we used a permutation test. For phenotype $i$ with the gene network of size $g_i$, we define $\beta_i$ as the slope derived by regressing the external degree distribution on the internal degree distribution. We then generate $n=1000$ networks of randomly selected genes of the same size $g_i$ as the set for phenotype $i$. Each random network is created by repeatedly generating networks of size $g_i$ and keeping non-zero genes. Once the number of non-zero genes is equal to $g_i$ we combine them into a single random network. For each random network $j$, we identify its slope $\beta_{r}$ representing the internal vs. external degree distribution regression line of random coherence. We calculate the permutation p-value as $p_i = \frac{(\sum_{j=1}^nI({\beta_{rj} > \beta_i}) + 1}{n + 1}$ [@Phipson:2010aa]. Intuitively, this approach estimates whether the slope of the phenotype-specific network $\beta_i$ is consistently larger than those of random networks. All analyses and visualizations were performed in the R/Bioconductor computing environment v.3.4.0 [@gentleman2006bioinformatics].
